Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-06-03 supplement.tex
Add Neand column to lineage probs

\begin{table}[ht]
\caption{
    \label{tab:supp-lineage-probabilitys}
    \textbf{Probability that a lineage sampled 500ya is found in a given branch.}
    Using our best-fit model (merger with stem migration), we calculated the probability
    that a lineage sampled in a given population (Nama, Mende, or Gumuz) is found in
    each branch at 10ka, 55ka, and 500ka. Lineages are sampled 500 years ago to
    avoid the effects of very recent admixture, such as recent European admixture in
    the Nama. Rows may not sum to one, as not every branch is listed here (such as
    Neanderthal).
}
\centering
\begin{tabular}[t]{lccccccc}
    \toprule
    & \specialcell{Nama\\branch} & \specialcell{Mende\\branch} &
    \specialcell{Gumuz\\branch} & \specialcell{Oromo/Amhara\\branch} & 
    \specialcell{British\\branch} & Stem 1 & Stem 2\\
    \midrule
    Found 10ka & & & & & & & \\
    Nama & 0.724 & 0.015 & 0.032 & 0.226 & 0.003 & & \\
    Mende & 0.003 & 0.881 & 0.058 & 0.058 & 0.001 & & \\
    Gumuz & 0.013 & 0.058 & 0.819 & 0.098 & 0.012 & & \\
    Oromo/Amhara & 0.013 & 0.058 & 0.098 & 0.819 & 0.012 & & \\
    \midrule
    Found 55ka & & & & & & & \\
    Nama & 0.677 & 0.052 & 0.264 & & & & 0.005 \\
    Mende & 0.021 & 0.562 & 0.272 & & & & 0.143 \\
    Gumuz & 0.060 & 0.211 & 0.704 & & & & 0.023 \\
    Oromo/Amhara & 0.041 & 0.142 & 0.793 & & & & 0.017 \\
    \midrule
    Found 500ka & & & & & & & \\
    Nama & & & & & & 0.379 & 0.618 \\
    Mende & & & & & & 0.430 & 0.569 \\
    Gumuz  & & & & & & 0.473 & 0.525 \\
    Oromo/Amhara & & & & & & 0.475 & 0.517 \\
    \bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[ht]
\caption{
    \label{tab:supp-lineage-probabilitys}
    \textbf{Probability that a lineage sampled 500ya is found in a given branch.}
    Using our best-fit model (merger with stem migration), we calculated the probability
    that a lineage sampled in a given population (Nama, Mende, or Gumuz) is found in
    each branch at 10ka, 55ka, and 500ka. Lineages are sampled 500 years ago to
    avoid the effects of very recent admixture, such as recent European admixture in
    the Nama.
}
\centering
\begin{tabular}[t]{lcccccccc}
    \toprule
    & \specialcell{Nama\\branch} & \specialcell{Mende\\branch} &
    \specialcell{Gumuz\\branch} & \specialcell{Oromo/Amhara\\branch} & 
    \specialcell{British\\branch} & Neand. & Stem 1 & Stem 2\\
    \midrule
    Found 10ka & & & & & & & \\
    Nama & 0.724 & 0.015 & 0.032 & 0.226 & 0.003 & & & \\
    Mende & 0.003 & 0.881 & 0.058 & 0.058 & 0.001 & & & \\
    Gumuz & 0.013 & 0.058 & 0.819 & 0.098 & 0.012 & & & \\
    Oromo/Amhara & 0.013 & 0.058 & 0.098 & 0.819 & 0.012 & & & \\
    \midrule
    Found 55ka & & & & & & & \\
    Nama & 0.677 & 0.052 & 0.264 & & & 0.002 & & 0.005 \\
    Mende & 0.021 & 0.562 & 0.272 & & & 0.001 & & 0.143 \\
    Gumuz & 0.060 & 0.211 & 0.704 & & & 0.002 & & 0.023 \\
    Oromo/Amhara & 0.041 & 0.142 & 0.793 & & & 0.008 & & 0.017 \\
    \midrule
    Found 500ka & & & & & & & & \\
    Nama & & & & & & 0.002 & 0.379 & 0.618 \\
    Mende & & & & & & 0.001 & 0.430 & 0.569 \\
    Gumuz  & & & & & & 0.002 & 0.473 & 0.525 \\
    Oromo/Amhara & & & & & & 0.008 & 0.475 & 0.517 \\
    \bottomrule
\end{tabular}
\end{table}
